---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Lab report #2

Follow the instructions posted at <https://ds202-at-isu.github.io/labs.html> for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.

All submissions to the github repo will be automatically uploaded for grading once the due date is passed. Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.



```{r}
#remotes::install_github("heike/classdata")
library(classdata)

```

```{r}
head(ames)
```

There are 16 variables in the Ames data set. Some variables are categorical and others are numerical.

```{r}
str(ames)
```

  
```{r}
library(ggplot2)
ames
View(ames)
library(tidyverse)

str(ames)


ames_filtered <- ames %>%
  filter(YearBuilt >= 1880 & YearBuilt <= 2022)
  
View(ames_filtered)
  
ggplot(ames_filtered, aes(x = YearBuilt, y = `Sale Price`)) +
  geom_histogram(stat = "identity", fill = "blue", alpha = 0.7) +  
  labs(title = "Histogram: Sale Price vs Year Built",
       x = "Year Built",
       y = "Sale Price") +
```


```{r}
theme_minimal()
```
  

Parcel ID: Character

Address: Character

Style: Factor

Occupancy: Factor

Sale Date: Date

Sale Price: Double

Multi Sale: Character

Year Built: Double

Acres: Double

Total Living Area: Double

Bedrooms: Double

Finished Basement Area: Double

Lot Area: Double

AC: Character

Fireplace: Character

Neighborhood: Factor

**Meaning of Variable:**

Parcel ID:

:   character with ID.

Address:

:   property address in Ames, IA.

Style:

:   factor variable detailing the type of housing.

Occupancy:

:   factor variable of type of housing.

Sale Date:

:   date of sale.

Sale Price:

:   sales price (in US dollar).

Multi Sale:

:   logical value: was this sale part of a package?

YearBuilt:

:   integer value: year in which the house was built.

Acres:

:   acres of the lot.

TotalLivingArea (sf):

:   total living area in square feet.

Bedrooms:

:   number of bedrooms.

FinishedBsmtArea (sf):

:   total area of the finished basement in square feet.

LotArea(sf):

:   total lot area in square feet.

AC:

:   logical value: does the property have an AC?

FirePlace:

:   logical value: does the property have an fireplace?

Neighborhood:

:   factor variable - levels indicate neighborhood area in Ames.

**Expected Range:**

This can be found in the summary output by subtracting the minimum from the maximum values for each applicable variable (some variable types do not have a range) in the summary output.

**Question 2)**

**is there a variable of special interest or focus?**

The special variable of focus is the sale price of the house/condo/apartment in USD.

**Question 3)**

**start the exploration with the main variable:**

-   **what is the range of the variable? draw a histogram for a numeric variable or a bar chart, if the variable is categorical. what is the general pattern? is there anything odd?**

-   **follow-up on oddities: see 4**

```{r}
max(ames$`Sale Price`,na.rm=TRUE)-min(ames$`Sale Price`,na.rm=TRUE)
```

The range for the sale price is 20500000 USD.

```{r}
ggplot(ames, aes(x = `Sale Price`)) + 
  geom_histogram() +
  ggtitle("Sale Price")
```

There is a lot of variance and a few outliners as there is large cluster near the y axis and a few outliers as you move right.

```{r}
#Ryan Riebesehl- I chose Acres
remotes::install_github('heike/classdata')
library(classdata)
head(ames)
```

```{r}

#Ryan Riebesehl- I chose Acres:
library(ggplot2)
ames1 <- na.omit(ames)
Acres <- ames1$Acres
SalePrice <- ames1$`Sale Price`
print(range(Acres))

ggplot(ames1, aes(x = Acres, y = SalePrice)) +
  geom_point(size = 3, alpha = 0.8) +
  labs(title = "Scatterplot of Sale Price against Related Variable",
       x = "Acres",
       y = "Sale Price",
       color = "Category") +
  theme_minimal()
```

\^Based on the scatter plot to see differences between Acres and Sales Price, you can see a slight trend that houses with small acres have an expensive sales price. This is the same for houses with large amounts Acres. This is probably because houses near the downtown city of Ames tend to be more expensive. Additionally, large acres of land will usually cost more money. There are some oddities in the graph as some price have not been updated.

