---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Lab report #2

Follow the instructions posted at <https://ds202-at-isu.github.io/labs.html> for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.

All submissions to the github repo will be automatically uploaded for grading once the due date is passed. Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.

```{r}
#remotes::install_github("heike/classdata")
library(classdata)

```

Installing and making sure classdata is up to date

Question 1)

```{r}
head(ames)
summary(ames)
```

There are 16 variables and they include: Parcel ID, Address, Style, Occupancy, Sale Date, Sale Price, Multi Sale, Year Built, Acres, Total Living Area, Bedrooms, Finished Basement Area, Lot Area, AC, Fireplace, Neighborhood.

Variable Type:

Parcel ID: Character

Address: Character

Style: Factor

Occupancy: Factor

Sale Date: Date

Sale Price: Double

Multi Sale: Character

Year Built: Double

Acres: Double

Total Living Area: Double

Bedrooms: Double

Finished Basement Area: Double

Lot Area: Double

AC: Character

Fireplace: Character

Neighborhood: Factor
